Deciding to Disclose: Pregnancy and Alcohol Misuse

### 2014-07-07 Model.tex
Filler
Filler text to be rewritten

In this section we outline the disclosure game model, and give details of the four decision rules.

A brief sketch of a pregnancy in terms of encounters between a woman and a midwife is instructive at this juncture. Typically women will have 12 appointments with a midwife during the antenatal period. Outside of caseloading teams, a woman does not generally have a named midwife, and may see a different practitioner at each appointment. In the UK, and unlike most healthcare scenarios, maternity notes are patient held, so midwives do not have extensive information prior to an appointment unless they have encountered the woman previously. Maternity notes are not generally linked to extra-departmental records, meaning that a history of alcohol related admissions to another service may remain unknown unless revealed by the woman.

@@

Beyond the booking appointment, the onus is on women to raise concerns about their drinking behaviour, or the midwife to probe further if they feel it is warranted.

@@

At the end of a game, each player receives a payoff dependent on the actions and types of both players, which has a partially common interest component. Women receive a payoff based on the health of their eventual baby, with a social cost dependent on the signal they sent and the midwife's reaction to it. Midwives receive the same health payoff as the women, but pay a cost for referring to a specialist, mirroring the organisational cost of non-routine care.

Taken together, this leads to a game tree that is relatively complex even at the subgame level (figure \ref{fig:subgame_tree} shows the subgame tree, with information sets). 
%The subgame has a large number of pure Nash equilibria, and solution using Gambit \citep{Gambit13}
Rather than attempt to solve for equilibria, agents treat this two player game as taking place against nature, along the lines of adversial risk analysis \citep{RiosInsua2009}. This effectively translates the game to a pair of decision problems, which agents attempt to resolve at each turn using a simple decision rule.

@@

Midwives play for \(k\) rounds (\(k=1000\) in all experiments), and conduct appointments in parallel. Unlike women, midwives are only informed of their payoff if they choose to make a referral. Both groups of agents have perfect recall, and midwives are assumed to retrospectively update their observations if they make a referral after a number of appointments.

@@

As noted in section \ref{sub:the_game}, agents have perfect recall, and recognise individual opponents if they encounter them subsequently. While agents recall perfectly and make use of the new information for retrospective updates, their decisions are made \'as-if\' they were facing a new opponent.

@@

Aside from the heuristic agent, the remaining three agent types use Bayesian updating to attempt to improve
the accuracy of their beliefs. Given the discrete nature of agent
types, and actions, coupled with a desire for tractability of the
simulation, the Dirichlet distribution is employed. The probability
density function takes the form -

@@

Where \(\alpha=\{\alpha_{1}\ldots\alpha_{k}\}\), \(k\)is the number
of discrete types, \(\Theta=\{x_{1},\,\ldots,x_{k-\text{1}}\}\) all
more than zero and summing to less than 1, and \(\alpha_{i}\) is the
psuedo-count of prior observations for type \(i\).

@@

Where \(n_{j}\) is simply the count of occurrences of type \(j\), so
that the belief that a new observation is of type \(j\) the number
of times that type has been observed (including the pseudo-count),
over the total number of observations thus far. This makes computation
of beliefs fast, and simple, since all that must be maintained is
a count of observations with no particular concern as to their order.

@@

@@

It would seem unreasonable to suppose that neither party recounts their experiences to their peers, and to explore the impact of this we also modify the game to introduce a simple form of information sharing within agent groups. This takes the form of having each agent share their memories with their colleagues with some probability \(p\). Individuals then incorporate shared information into their beliefs using weighted updates, such that a shared observation of a low type signal contributes to their beliefs by \(q\), and \(0\leq q\leq 1\). Women share only when they have finished play, and provide their complete history of games, because they have accurate information about the outcomes. By the same rationale, midwives share only their history with the most recent woman they referred. Sharing occurs simultaneously for all players at the end of each round, and all memories are either shared immediately or discarded.\footnote{Memories of games remain, but it is assumed that only current news is relevant.}

Because of their differing problem representations, the simple payoff reasoners and their more complex counterparts incorporate this outside information differently. The simple payoff based rule relys on a belief structure relating actions directly to rewards. Because payoffs differ by the agent's private type, the information shared may not correspond to the experience of the listening agent in the same scenario. As a result, payoff reasoners have a belief bias towards the most common player type, and can believe in outcomes that are, for them, impossible.

@@

\subsection{Model Implementation}
\label{sub:the_code}
% Use this bit to talk about the practical version of the game and where info is revealed?
The model itself is implemented as a Python module, and is freely available under the Mozilla Public License from \url{https://github.com/greenape/disclosure-game}, together with full parameter sets, raw data, and all other code used in producing this paper.

>>>>

In this section we outline the disclosure game model, and give details of the four decision rules, but begin with a brief sketch of a pregnancy in terms of encounters between a woman and a midwife. 
Typically women will have 12 appointments with a midwife during the antenatal period. Outside of caseloading teams, a woman does not generally have a named midwife, and may see a different practitioner at each appointment. In the UK, and unlike most healthcare scenarios, maternity notes are patient held, so midwives do not have extensive information prior to an appointment unless they have encountered the woman previously. Maternity notes are not generally linked to extra-departmental records, meaning that a history of alcohol related admissions to another service may remain unknown unless revealed by the woman.

@@

Beyond the booking appointment, the onus is on women to raise concerns about their drinking behaviour, or the midwife to probe further if they feel it is warranted. In either case, once a concern has been raised the midwife must respond clinically, and inevitably personally, to the information.

In an ideal world, all interactions with healthcare providers would be immediately and fully disclosive, with no repercussions for the patient. However even when considering less emotive topics, this is not the case.

@@

At the end of a game, each player receives a payoff dependent on the actions and types of both players, which has a partially common interest component. Women receive a payoff based on the health of their eventual baby, with a social cost dependent on the signal they sent and the midwife's reaction to it. Midwives receive the same health payoff as the women, but pay a cost for referring to a specialist, mirroring the organisational cost of non-routine care (table \ref{tab:Payoff-matrix}).

Taken together, this leads to a game tree that is relatively complex even at the subgame level (figure \ref{fig:subgame_tree} shows the extensive form for a subgame, with information sets). 
%The subgame has a large number of pure Nash equilibria, and solution using Gambit \citep{Gambit13}
Rather than attempt to solve for equilibria, agents treat this two player game as taking place against nature, along the lines of adversial risk analysis \citep{RiosInsua2009}. This effectively translates the game to a pair of decision problems, which agents attempt to resolve at each turn using a simple decision rule, given their prior beliefs and experience of play.

@@

Midwives play for \(k\) rounds (\(k=1000\) in all experiments), and conduct appointments in parallel, i.e. if there are 5 midwives, then five women are drawn from the queue and assigned at random to the midwives. 
Unlike women, midwives are only informed of their payoff if they choose to make a referral. Both groups of agents have perfect recall, and midwives are assumed to retrospectively update their observations if they make a referral after a number of appointments.

\begin{table}
\center
\subfloat[Social cost\label{tab:Social-cost-matrix}]{%
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5} 
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline

\hline
\multirow{4}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
\cline{2-5} 
 & Harsh & 0, -2 & 0, -1 & 0, 0\tabularnewline
\cline{2-5} 
 & Medium & 0, -1 & 0, 0 & 0, 0\tabularnewline
\cline{2-5} 
 & Low & 0, 0 & 0, 0 & 0, 0\tabularnewline
\hline 
\end{tabular}

}

\subfloat[Health outcome\label{tab:Referral-payoff-matrix}]{%
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5} 
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline

\hline 
\multirow{3}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
\cline{2-5} 
 & Refer & 10, 10 & 10, 10 & 10, 10\tabularnewline
\cline{2-5} 
 & Don't refer & -2, -2 & -1, -1 & 10, 10\tabularnewline
\hline 
\end{tabular}

}

\subfloat[Referral cost\label{tab:inst_cost_matrix}]{%
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5}  
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline
\hline 
\multirow{3}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
\cline{2-5} 
 & Refer & -9, 0 & -9, 0 & -9, 0\tabularnewline
\cline{2-5} 
 & Don't refer & 0, 0 & 0, 0 & 0, 0\tabularnewline
\hline 
\end{tabular}

}

\caption{Payoff matrices\label{tab:Payoff-matrix}}
\end{table}

@@

As noted in section \ref{sub:the_game}, agents have perfect recall, and recognise individual opponents if they encounter them subsequently. While agents recall perfectly and make use of the new information for retrospective updates, all four agent models make decisions `as-if' they were always facing a new opponent.

@@

Aside from the heuristic agent, the remaining three agent types use Bayesian updating to attempt to improve
the accuracy of their beliefs. Given the discrete nature of agent
types, and actions, coupled with a desire for tractability of the
simulation, the Dirichlet distribution is employed to represent these beliefs. The probability
density function takes the form -

@@

Where \(\alpha=\{\alpha_{1}\ldots\alpha_{k}\}\), \(k\) is the number
of discrete types, \(\Theta=\{x_{1},\,\ldots,x_{k-\text{1}}\}\) all
more than zero and summing to less than 1, and \(\alpha_{i}\) is the integer
psuedo-count of prior observations for type \(i\).

@@

Where \(n_{j}\) is simply the count of occurrences of type \(j\), so
that the belief that a new observation is of type \(j\) the number
of times that type has been observed (including the pseudo-count),
over the total number of observations thus far. This makes computation
of beliefs fast and simple, since all that must be maintained is
a count of observations with no particular concern as to their order.

@@

Rather than the psychologically more interesting \ac{PT}, the \ac{CPT}
decision rule is used in this instance, because of the requirement
for women to evaluate more than two `prospects'.\footnote{A prospect in this instance is a paired outcome and probability, and the set of prospects
for an action hence define the outcome space.} \ac{CPT} introduces
the concept of a probability weighting function, which underweights
small probabilities, and overweights large ones in an effort to capture
the tendency of humans to treat high probability events as sure things,
and small probabilities as `never going to happen'. A number of different
weighting functions have been proposed, but in this instance the original
formulation by \citet{Tversky1992} is used. This distinguishes between
weighting for gains, and losses -

\begin{eqnarray*}
w^{+}(p) & = & \frac{p^{\gamma}}{(p^{\gamma}+(1-p)^{\gamma})^{\frac{1}{\gamma}}}\\
w^{-}(p) & = & \frac{p^{\delta}}{(p^{\delta}+(1-p)^{\delta})^{\frac{1}{\delta}}}
\end{eqnarray*}

Where $p$ is the unweighted probability, and $\gamma$ and $\delta$
are the weights for gain and loss probabilities respectively. Humans
have also been observed to value gains and losses differently, with
a loss being `worse' than the equivalent gain is `good'. This
entails a transformed value function -

\[
v(x)=\begin{cases}
f(x) & if\, x>0\\
0 & if\, x=0\\
g(x) & if\, x<0
\end{cases}
\]

Where,

\[
f(x)=\begin{cases}
x^{\alpha} & if\,\alpha>0\\
ln(x) & if\,\alpha=0\\
1-(1+x)^{\alpha} & if\,\alpha<0
\end{cases}
\]
\[
g(x)=\begin{cases}
-(-x)^{\beta} & if\,\beta>0\\
-ln(-x) & if\,\beta=0\\
(1-x)^{\beta}-1 & if\,\beta<0
\end{cases}
\]

And $\alpha$, and $\beta$ are respectively the power of a gain,
and a loss. The \ac{CPT} value of outcome $x$ is $v(x)w^{+}(x)$
if $x\geq0$, and $v(x)w^{-}(x)$ otherwise. For an action the \ac{CPT}
value is the sum of the value of the prospects of that action, as
in the Bayesian risk model. The decision rule then requires the agent
to choose the action which maximises the prospect theory value.

@@

It would seem unreasonable to suppose that neither party recounts their experiences to their peers, and to explore the impact of this we also modify the game to introduce a simple form of information sharing within agent groups. This takes the form of having each agent share their memories with their colleagues with some probability \(p\). Individuals then incorporate shared information into their beliefs using weighted updates, such that a shared observation of a low type signal contributes to their beliefs by \(q\), and \(0\leq q\leq 1\) (i.e. \(n_{j} = n_{j} + q\)).
Women share only when they have finished play, and provide their complete history of games, because they have accurate information about the outcomes. By the same rationale, midwives share only their history with the most recent woman they referred. Sharing occurs simultaneously for all players at the end of each round, and all memories are either shared immediately or discarded.\footnote{Memories of games remain, but it is assumed that only current news is relevant.}

Because of their differing problem representations, the simple payoff reasoners and their more complex counterparts incorporate this exogenous information differently. The simple payoff based rule relys on a belief structure relating actions directly to rewards. Because payoffs differ by the agent's private type, the information shared may not correspond to the experience of the listening agent in the same scenario. As a result, payoff reasoners have a belief bias towards the most common player type, and can believe in outcomes that are, for them, impossible.

@@
